\documentclass[a4paper,11pt,oneside,openany,uplatex]{jsbook}
%
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{theorem}
\usepackage{bm}
\usepackage{ascmac}
\usepackage{subfigure}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{mediabb}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{cite}
\usepackage{layout}
\usepackage{verbatim}
\usepackage{wrapfig}
\usepackage{ascmac}
\usepackage{makeidx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}


% \includeonly{evaluation}

% \usepackage[top=30truemm,bottom=30truemm,left=25truemm,right=25truemm]{geometry}
%\usepackage{times, mathptm}
%
\renewcommand{\baselinestretch}{1.0}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Table.}
\renewcommand{\headfont}{\bfseries}

\makeindex

\setlength{\textwidth}{150truemm}
\setlength{\fullwidth}{\textwidth}
\setlength{\oddsidemargin}{30truemm}   % 左余白
\addtolength{\oddsidemargin}{-1truein} % 左位置デフォルトから-1inch
\setlength{\topmargin}{30truemm}       % 上余白
\setlength{\textheight}{227truemm}     % テキスト高さ: 297-(30+30)=237mm
\addtolength{\topmargin}{-1truein}     % 上位置デフォルトから-1inch
\setlength{\voffset}{-0.55in}
\makeatletter
%
\def\thesis{Master Thesis}
\def\gakui{2014年度　修士論文}
\def\title#1{\def\title{#1}}
\def\daimoku#1{\def\daimoku{#1}}
\def\id#1{\def\id{#1}}
\def\department#1{\def\department{#1}}
\def\shozoku#1{\def\shozoku{#1}}
\def\author#1{\def\author{#1}}
\def\chosha#1{\def\chosha{#1}}
\def\submission#1{\def\@submission{#1}}
\def\teacher#1{\def\teacher{#1}}
%
\def\maketitlea{
\begin{center}
{\huge \thesis \par} 
\vspace{10mm}
{\huge \gakui \par} 
\vspace{10mm}
{\LARGE \daimoku \par}% 論文のタイトル部分
\vspace{10mm}
{\Large \title \par} %
\vspace{10mm}
{\Large \@submission \par} %
\vspace{15mm}
{\Large \shozoku \par} 
{\Large \id \chosha \par} % 学籍番号部分
\vspace{10mm}
{\Large 指導教員  \teacher \par}
\vspace{10mm}
{\Large \department \par}
\vspace{10mm}
{\LARGE \author}
\end{center}
%\par\vskip 1.5em
\clearpage
}
%
\daimoku{Multipath TCPによる経路切り替え手法を用いた \\ データセンターネットワークにおける \\ ショートフロー完結時間の改善}
\title{Improving the flow completion time of short flows in datacenter network
with path switching by Multipath TCP}
\date{\today}
\shozoku{東京大学大学院 \\ 工学系研究科 電気系工学専攻}
\department{The University of Tokyo \\ Graduate School of Engineering,
Department of Electrical Engineering and Information Systems}
\id{37-136482}
\chosha{藤居 翔吾}
\author{Shogo Fujii}
\submission{平成26年 2月5日 提出}
\teacher{関谷 勇司}

%%%%%%%%%%%%%%%%%%%%%%%%
\makeatother
%

\begin{document}
%
\pagestyle{empty}
\maketitlea


\begin{center}
{\large {\bf 要旨}}
\end{center}
クラウド型のサービスの性質により, 今日のデータセンターではデータセンター内のトラフィックが増大しており,
複数の経路を持つネットワーク環境を応用して, 通信性能向上を目指す取り組みがされている.
しかし, 様々なニーズを抱えるトラフィックが混在している中で, レイテンシ志向なサイズの小さいフローに対し,
既存のMPTCP実装では性能を劣化させる問題が報告されている.
そこで本研究では, この問題に対し, 並列分散処理アプリケーションが稼働しているクラスターPCのトラフィックを観測する事で, 単一NIC(Network
Interface Card)への通信集中によるキュー負荷の影響があることを検討し,
サイズの大きいスループット指向なロングフローとサイズの小さいレイテンシ指向なショートフローが一つのリンクに混在して通信を行っていることを明らかにし,
それによる通信性能障害が生じる技術的背景を考察した. 
そして, フローの指向毎に異なる通信経路を利用するレーンモデルを提案した. 
また, OSレベルから一つの通信を見た際に, そのフローの指向をフロー持続時間を用いて分類し, 経路の状況に合わせた経路切替手法を提案した. 
提案手法をOSに実装し, シミュレーションを用いた評価を行い, ロングフローとショートフローが混在する環境下で,
それぞれの指向毎に経路を切り替える制御を行うことで, ショートフロー通信を短縮化ならびに, ロングフローの通信性能を改善することを示した. 


\vspace{5mm}

\begin{center}
{\large \bf Abstract}
\end{center}
As increasing the amount of traffic in a datacenter by cloud service, the
effective network for utilization of massive computer clusters has been studied.
Recently, Multipath TCP(MPTCP) has been tackled this problem.
MPTCP can achieve the effective consumptions of the resources with multipath,
but a researcher reported MPTCP causes the delay of flow completion for short
flows in such a multipath network environment.
In this paper, I presented measurements of the distribute processing cluster
PCs and reveal impairment mechanisms that lead to that latencies, rooted in single
NIC(Network Interface Card) with intensive load traffic. 
I revealed there are both latency-oriented short flow and throughput-oriented long flow in a datacenter network. 
As the result, they lead to the performance impairment in flow completion time. 
In order to solve this problem, I proposed datacenter lane model to utilize different paths for each requirement of the flow. 
I developed the method of flow-classification for the orient and path-switching scheme to react the path condition with flow duration time, as approach just for end-node. 
I implemented these techniques to the end-node OS, and evaluated by simulation experiment. 
In my experiment, my proposals improve the performance for short flow in
shortening the FCT and long flow in increasing throughput with the control to separate the mixture traffic into both latency oriented flow and throughput-oriented one.

\clearpage

\frontmatter
\pagestyle{headings}
\tableofcontents 
\clearpage

\frontmatter
\pagestyle{headings}
\listoffigures
\clearpage


\frontmatter
\pagestyle{headings}
\listoftables
\clearpage



\mainmatter
\pagestyle{headings}

\include{introduction}

\include{related_work}

\include{datacenter_network}

\include{motivated_work}

\include{proposal}

\include{evaluation}

\include{consideration}

\include{conclusion}

\include{my_work}

\include{thanks}


\vspace{1cm}
\begin{thebibliography}{99}
\bibitem{IBM_rep}{日本アイ・ビー・エム株式会社. IBM 第1章
大容量データのバックアップ,
\url{http://www-06.ibm.com/systems/jp/storage/column/backup/01.html}}
\bibitem{amazon}{Jim Liddle. Amazon found every 100ms of latency cost them 1\%
in sales, August 2008.
\url{http://blog.gigaspaces.com/amazon-found-every-100ms-of-latency-cost-them-1-in-sales/}}

\bibitem{customer_impact}{R. Kohavi et al. Practical Guide to Controlled
Experiments on theWeb: Listen to Your Customers not to the HiPPO. KDD, 2007.}
\bibitem{requirement}{J. Hamilton. On designing and deploying Internet-scale
services. In USENIX LISA, 2007.}
\bibitem{presto}{Facebook. Presto: Interacting with petabytes
of data at Facebook,
\url{https://www.facebook.com/notes/facebook-engineering/presto-interacting-with-petabytes-of-data-at-facebook/10151786197628920}}
\bibitem{mapreduce}{Dean, Jeffrey, and Sanjay
Ghemawat. "MapReduce: simplified data processing on large clusters." Communications of the ACM 51.1 (2008): 107-113.}
\bibitem{fattree}{Al-Fares, Mohammad, Alexander L oukissas, and Amin Vahdat. "A
scalable, commodity data center network architecture." ACM SIGCOMM Computer
Communication Review. Vol. 3}
\bibitem{dctcp}{Alizadeh, Mohammad, et al. "Data center tcp (dctcp)." ACM SIGCOMM Computer Communication Review 40.4 (2010): 63-74.}
\bibitem{improving}{Raiciu, Costin, et al. "Improving datacenter performance and
robustness with multipath TCP." ACM SIGCOMM Computer Communication Review. Vol. 41. No. 4. ACM, 2011.}
\bibitem{detail}{Zats, David, et al. "DeTail: Reducing the flow completion time
tail in datacenter networks." ACM SIGCOMM Computer Communication Review 42.4 (2012): 139-150.}
\bibitem{p_fab}{Alizadeh, Mohammad, et al. "pfabric: Minimal near-optimal datacenter transport." Proceedings of the ACM SIGCOMM 2013 conference on SIGCOMM. ACM, 2013.}
\bibitem{click}{Kohler, Eddie, et al. "The Click modular router." ACM
Transactions on Computer Systems (TOCS) 18.3 (2000): 263-297.}
\bibitem{mptcp}{Ford, Alan, et al. TCP Extensions for Multipath Operation with
Multiple Addresses: draft-ietf-mptcp-multiaddressed-03. No. Internet draft (draft-ietf-mptcp-multiaddressed-07). Roke Manor, 2011.}
\bibitem{traffic}{Benson, Theophilus, Aditya Akella, and David A. Maltz.
"Network traffic characteristics of data centers in the wild." Proceedings of the 10th ACM SIGCOMM conference on Internet measurement. ACM, 2010.}
\bibitem{NAPI}{J. Salim, When NAPI Comes to Town, Proceedings of Linux 2005
Conference, UK, August 2005.}
\bibitem{RSS}{Microsoft corporation. scalable networking with rss, 2005.}
\bibitem{RFS}{Herbert, T. rfs: receive flow steering, september 2010.
http://lwn.net/Articles/381955/.} 
\bibitem{RPS}{Herbert, T. rps: receive packet steering, september 2010.
\url{http://lwn.net/Articles/361440/.}}
\bibitem{mptcp_linux}{ip networking lab「MultiPath TCP - Linux Kernel
implementation」\url{http://mptcp.info.ucl.ac.be/}} 
\bibitem{rtt}{Vasudevan, Vijay, et al. "Safe and effective fine-grained TCP
retransmissions for datacenter communication." ACM SIGCOMM Computer Communication Review. Vol. 39. No. 4. ACM, 2009.}
\bibitem{mptcp_ana}{藤居 翔吾, 田崎 創, 関谷 勇司, "MultiPath TCP
適用時のデータセンターネットワークでのフローサイズが与える影響に関する一考察", 電子情報通信学会, 信学技法, vol. 113, no. 364,
IA2013-65, pp. 47-52, 2013.}
\bibitem{mptcp_ana2}{藤居翔吾, 田崎創, 関谷勇司, "MultiPath TCP 適用時のデータセンター
ネットワークでのフローサイズが与える影響に関する一考察", 日本ソフトウェア科学会研究会資料シリーズ No.74 ISSN1341-870X,
インターネットコンファレス2014論文集, pp33-42 } 
\bibitem{flexible}{P. Agarwal, B. Kwan, and L. Ashvin. Flexible buffer allocation entities for
traffic aggregate containment. US Patent 20090207848, August 2009.}
\bibitem{synchro}{S. Floyd and V. Jacobson. The synchronization of periodic routing messages.
IEEE/ACM ToN, 1994.}
\bibitem{balia}{A. Walid, et al. Balanced Linked Adaptation Congestion Control
Algorithm for MPTCP draft-walid-mptcp-congestion-control-00, 2014.}
\bibitem{tcpdump}{tcpdump, \url{http://www.tcpdump.org/}}
\bibitem{intel}{intel,
\url{http://www.intel.com/content/www/us/en/network-adapters/gigabit-network-adapters/ethernet-server-adapters.html}}
\bibitem{bottleneck}{Lu, Guohan, et al. "Using cpu as a traffic co-processing
unit in commodity switches." Proceedings of the first workshop on Hot topics in software defined networks. ACM, 2012.}
\bibitem{sctp}{R. Stewart. Stream Control Transmission Protocol. RFC 4960
(Proposed Standard), September 2007. Updated by RFCs 6096, 6335. }
\bibitem{cmt_1}{Iyengar, Janardhan R., Paul D. Amer, and Randall Stewart.
"Concurrent multipath transfer using SCTP multihoming over independent end-to-end paths." Networking, IEEE/ACM Transactions on 14.5 (2006): 951-964.}
\bibitem{cmt_2}{Iyengar, Janardhan, et al. "Concurrent multipath transfer using
SCTP multihoming." SPECTS 2004 (2004).}
\bibitem{lacp}{IEEE Standards Association. "IEEE 802.3 LAN/MAN CSMA/CD Access
Method." (2008).}
\bibitem{lacp_problem}{Fukunaga, Takafumi, and Hidenori Umeno. "Implementation
and evaluation of improvement in parallel processing performance on the cluster using small-scale SMP PCs." IEEJ Transactions on Electronics, Information and Systems 128 (2008): 1842-1851.}
\bibitem{arp}{Umeshima S, Higaki H. Extended ARP for high-per-
formance LAN communications with multiple kinds
of NICs. 2003-DSM-029, Vol. 2003, No. 38, p 31–36,
2003.}
\bibitem{oldi}{Meisner, David, et al. "Power management of online data-intensive
services." Computer Architecture (ISCA), 2011 38th Annual International Symposium on. IEEE, 2011.}
\bibitem{incast}{Chen, Yanpei, et al. "Understanding TCP incast throughput
collapse in datacenter networks." Proceedings of the 1st ACM workshop on Research on enterprise networking. ACM, 2009.}
\bibitem{desynchro}{Floyd, Sally, and Van Jacobson. "The synchronization of
periodic routing messages." Networking, IEEE/ACM Transactions on 2.2 (1994): 122-136.}
\bibitem{memory}{Iyer, Sundar, Ramana Rao Kompella, and N. McKeowa. "Analysis of
a memory architecture for fast packet buffers." High Performance Switching and Routing, 2001 IEEE Workshop on. IEEE, 2001.}
\bibitem{websearch}{Barroso, Luiz André, Jeffrey Dean, and Urs Holzle. "Web
search for a planet: The Google cluster architecture." Micro, Ieee 23.2 (2003): 22-28.}
\bibitem{d3}{Wilson, Christo, et al. "Better never than late: Meeting deadlines
in datacenter networks." ACM SIGCOMM Computer Communication Review. Vol. 41. No. 4. ACM, 2011.}
\bibitem{d2tcp}{Vamanan, Balajee, Jahangir Hasan, and T. N. Vijaykumar.
"Deadline-aware datacenter tcp (d2tcp)." ACM SIGCOMM Computer Communication Review 42.4 (2012): 115-126.}
\bibitem{key-value1}{Beaver, Doug, et al. "Finding a Needle in Haystack:
Facebook's Photo Storage." OSDI. Vol. 10. 2010.}
\bibitem{key-value2}{Hastorun, Deniz, et al. "Dynamo: Amazon’s highly available
key-value store." In Proc. SOSP. 2007.}
\bibitem{dryad}{Isard, Michael, et al. "Dryad: distributed data-parallel
programs from sequential building blocks." ACM SIGOPS Operating Systems Review. Vol. 41. No. 3. ACM, 2007.}
\bibitem{repflow}{Liu, Shuhao, et al. "RepFlow on node. js: Cutting Tail Latency
in Data Center Networks at the Applications Layer." arXiv preprint arXiv:1407.1239 (2014).}
\bibitem{vl2}{Greenberg, Albert, et al. "VL2: a scalable and flexible data
center network." ACM SIGCOMM Computer Communication Review. Vol. 39. No. 4. ACM, 2009.}
\bibitem{devoflow}{Curtis, Andrew R., et al. "Devoflow: scaling flow management
for high-performance networks." ACM SIGCOMM Computer Communication Review. Vol. 41. No. 4. ACM, 2011.}
\bibitem{clos}{Clos, Charles. "A Study of Non‐Blocking Switching Networks." Bell
System Technical Journal 32.2 (1953): 406-424.}
\bibitem{bpr}{U.S. Department of Commerce, Bureau of Public Roads(1964),
Traffic Assignment Manual}
\bibitem{davidson}{Davidson, K. B. "A flow travel time relationship for use in
transportation planning." Australian Road Research Board (ARRB) Conference, 3rd, 1966, Sydney. Vol. 3. No. 1. 1966.}
\bibitem{ns3}{Tazaki, Hajime, et al. "Direct code execution: Revisiting library
os architecture for reproducible network experiments." Proceedings of the ninth ACM conference on Emerging networking experiments and technologies. ACM, 2013.}
\bibitem{crossbar}{McKeown, Nick. "A fast switched backplane for a
gigabit switched router." Business Communications Review 27.12 (1997): 1-30.}
\bibitem{delay}{Priority flow control: Build reliable layer 2 infrastructure.
\url{http://www.cisco.com/en/US/prod/collateral/switches/
ps9441/ps9670/white_paper_c11-542809.pdf}}
\bibitem{pdq}{Hong, Chi-Yao, Matthew Caesar, and P. Godfrey. "Finishing flows
quickly with preemptive scheduling." ACM SIGCOMM Computer Communication Review 42.4 (2012): 127-138.}
\bibitem{survey}{Liu, Shuhao, Hong Xu, and Zhiping Cai. "Low latency datacenter
networking: A short survey." arXiv preprint arXiv:1312.3455 (2013).}
\bibitem{hull}{Alizadeh, Mohammad, et al. "Less is more: trading a little
bandwidth for ultra-low latency in the data center." Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation. USENIX Association, 2012.}
\bibitem{dibs}{Zarifis, Kyriakos, et al. "DIBS: just-in-time congestion
mitigation for data centers." Proceedings of the Ninth European Conference on Computer Systems. ACM, 2014.}
\bibitem{fastlane}{Zats, David, et al. FastLane: An agile congestion signaling
mechanism for improving datacenter performance. No. UCB/EECS-2013-113. CALIFORNIA UNIV BERKELEY DEPT OF ELECTRICAL ENGINEERING AND COMPUTER SCIENCE, 2013.}
\bibitem{cp}{Cheng, Peng, et al. "Catch the whole lot in an action: Rapid
precise packet loss notification in data centers." Proc. USENIX NSDI. 2014.}
\bibitem{mcp}{Chen, Li, et al. "Towards minimal-delay deadline-driven data
center tcp." Proceedings of the Twelfth ACM Workshop on Hot Topics in Networks. ACM, 2013.}
\bibitem{bcube}{Guo, Chuanxiong, et al. "BCube: a high performance,
server-centric network architecture for modular data centers." ACM SIGCOMM Computer Communication Review 39.4 (2009): 63-74.}
\bibitem{cong}{Raiciu, C., M. Handley, and D. Wischik. "Coupled congestion
control for multipath transport protocols." draft-ietf-mptcp-congestion-01 (work in progress) (2011).}
\bibitem{RTT_est}{Jacobsson, Krister, et al. "Round trip time estimation
in communication networks using adaptive kalman filtering." (2004).}
\bibitem{queue_delay}{Angrisani, Leopoldo, et al. "Measurement of processing and
queuing delays introduced by an open-source router in a single-hop network."
Instrumentation and Measurement, IEEE Transactions on 55.4 (2006): 1065-1076.}
\bibitem{trouble}{DEAN, J. Software engineering advice from building large-scale distributed systems. http://research.google.com/people/jeff/stanford-295-talk.pdf.
}
\bibitem{openflow}{McKeown, Nick, et al. "OpenFlow: enabling innovation in
campus networks." ACM SIGCOMM Computer Communication Review 38.2 (2008): 69-74.}
\end{thebibliography}
\clearpage
\def\thesection{}
\def\thesubsection{\Alph{subsection}}
\def\thesection{付録\Alph{section}}
\setcounter{subsection}{0}
\appendix
\section{リンクパフォーマンス関数:Davidson関数}
リンクパフォーマンス関数は, ネットワークを構成する個々のリンクのサービス水準をリンク交通量とリンク属性の関数として表したものである. 
本研究では, リンクのサービス水準には, フロー完結時間(旅行時間)を用いている. 
リンクパフォーマンス関数は, 狭義の増加関数である必要があり, このことは待ち行列理論を用いて説明することができる. 

今, M/M/1($\infty$)の待ち行列理論を考える. 
この時, 到着率$\lambda$, サービス率$\mu$を用いて利用率$\rho$は以下のように表される. 

\begin{equation}
\label{utilization}
\rho = \frac{\lambda}{\mu}
\end{equation}

この利用率$\rho$と平均サービス時間$T_s$を用いて, 待ち時間$T_w$は以下のように表される. 
\begin{equation}
\label{traffic}
T_w = \frac{\rho}{1-\rho} \times T_s
\end{equation}

次にあるリンクにおけるフロー完結時間$t$を導出する. 
このリンクにおいて, 他のフローが存在しない時のフロー完結時間を$t_0$とする. 
この時, 遅れのパラメータ$J(>0)$と式\ref{utilization}, \ref{traffic}を用いて以下のように表すことができる. 
\begin{equation}
\label{delay}
J t_0 \frac{\rho}{1-\rho} = J t_0 \frac{q}{C-q} 
\end{equation}
ここで, $q$はリンク利用率, $C$はリンク容量である.
これにより, フロー完結時間$t(q)$は次のように定義される. 
\begin{eqnarray}
t(q) = t_{0} + J t_{0} \frac{\rho}{1-\rho} = t_{0}\Bigl\{ 1 + J \bigl(
\frac{q}{C-q} \bigr) \Bigr\}
\end{eqnarray}


\end{document}